Characteristic polynomials of p-adic matrices

### 2017-01-31 charpoly/charpoly.tex
More on statistics

\subsection{$\com (X -H)$ and flat precision}

@@

\subsection{Computation and optimal jagged precision}

@@

\noindent {\bf Algorithm 3:} {\tt Approximate $\com (X -M)$ }

@@

\subsection{Optimal jagged precision}

\section{Eigenvalues}
\label{sec:eigenvalues}

\subsection{Optimal precision on a simple eigenvalue}

>>>>

\subsection{The comatrix of $X{-}H$}

@@

\subsection{The comatrix of $X{-}M$}

\todo{Add a small intro}

@@

\noindent {\bf Algorithm 3:} {\tt Approximate $\com (X{-}M)$ }

@@

\section{Optimal jagged precision}

\subsection{On the characteristic polynomial}

\todo{Reorganize...}

{\bf Numerical experiments}

\begin{figure}
\hfill
{\renewcommand*{\arraystretch}{1.3}
\begin{tabular}{|c|r|r|r|}
\cline{2-4} 
\multicolumn{1}{l|}{} 
  & \multicolumn{3}{c|}{Average loss of accuracy} \\
\cline{2-4}
\multicolumn{1}{l|}{\null\hspace{6mm}\null} 
  & \makebox[1.5cm]{\hfill Optimal\hfill\null}
  & \makebox[1.5cm]{\hfill CR\hfill\null}
  & \makebox[1.5cm]{\hfill FP\hfill\null} \\
\hline
\rule{0pt}{2.7ex}%
$X^0$ & $3.17$ & $196\phantom{.00}$ & $189\phantom{.00}$ \vspace{-1.5ex} \\
{\scriptsize (det.)} 
& {\scriptsize dev: $1.76$} & {\scriptsize dev: $240$} & {\scriptsize dev: $226$} \\
\rule{0pt}{2.7ex}%
$X^1$ & $2.98$ & $161\phantom{.00}$ & $156\phantom{.00}$ \vspace{-1.5ex} \\
& {\scriptsize dev: $1.69$} & {\scriptsize dev: $204$} & {\scriptsize dev: $195$} \\
\rule{0pt}{2.7ex}%
$X^2$ & $2.75$ & $129\phantom{.00}$ & $126\phantom{.00}$ \vspace{-1.5ex} \\
& {\scriptsize dev: $1.57$} & {\scriptsize dev: $164$} & {\scriptsize dev: $164$} \\
\rule{0pt}{2.7ex}%
$X^3$ & $2.74$ & $108\phantom{.00}$ & $105\phantom{.00}$ \vspace{-1.5ex} \\
& {\scriptsize dev: $1.73$} & {\scriptsize dev: $144$} & {\scriptsize dev: $143$} \\
\rule{0pt}{2.7ex}%
$X^4$ & $2.57$ &  $63.2\phantom{0}$ &  $60.6\phantom{0}$ \vspace{-1.5ex} \\
& {\scriptsize dev: $1.70$} & {\scriptsize dev: $85.9$} & {\scriptsize dev: $85.8$} \\
\rule{0pt}{2.7ex}%
$X^5$ & $2.29$ &  $51.6\phantom{0}$ &  $49.7\phantom{0}$ \vspace{-1.5ex} \\
& {\scriptsize dev: $1.66$} & {\scriptsize dev: $75.3$} & {\scriptsize dev: $74.9$} \\
\rule{0pt}{2.7ex}%
$X^6$ & $2.07$ &   $9.04$           &   $8.59$ \vspace{-1.5ex} \\
& {\scriptsize dev: $1.70$} & {\scriptsize dev: $26.9$} & {\scriptsize dev: $26.4$} \\
\rule{0pt}{2.7ex}%
$X^7$ & $1.64$ &   $5.70$           &   $5.38$ \vspace{-1.5ex} \\
& {\scriptsize dev: $1.65$} & {\scriptsize dev: $15.3$} & {\scriptsize dev: $14.7$} \\
\rule{0pt}{2.7ex}%
$X^8$ & $0.99$ &   $0.99$           &   $0.99$ \vspace{-1.5ex} \\
{\scriptsize (trace)} 
& {\scriptsize dev: $1.37$} & {\scriptsize dev: $1.37$} & {\scriptsize dev: $1.37$} \\
\hline
\end{tabular}}
\hfill\null

\hfill
{\footnotesize Results for a sample of $1000$ instances}
\hfill\null

\caption{Average loss of accuracy on the coefficients
of the characteristic polynomial of a random $9 \times 9$
matrix over $\Q_2$}

\end{figure}

\subsection{On eigenvalues}
\label{ssec:eigenvalues}
